Here we will present some possible scenarios in which the service is involved.
\section{Scenario 1}
Al has to come back home and there are no more bus available. He opens the PowerEnjoy app on his smartphone. The app, using the phone GPS, shows Al all the cars close to him. Al finds a car 50m close and reserves it. Once he reaches it he asks to the system to open it. Once he enters he submit his password on car the tablet present on the car and starts the ride. Al find the safe area nearest his house, parks the car there and ends the ride. The system calculate the bill and charges it to Al's account.
\section{Scenario 2}
Al, John and Jack have to go to the airport. They meet at Al's house. Al finds and books a car. They reach the car and enter into it. Car sensor counts two passengers excluding the driver. When the ride ends a discount of 10\% will be applied before the system charges the fee to Al's account.
\section{Scenario 3}
Similar to scenario 2 Al, John and Jack go to the airport with the same car. Once they enter into the car, Al selects the money saving option before they start moving. The system shows him the position of the power grid stations near their destination and Al picks up one. Once Al parks and connects the car to the power grid a discount of 40\% will applied to the total bill (10\% because there were two passenger excluding the diver and 30\% because Al connected the car to the power grid).
\section{Scenario 4}
Similar to scenario 2 Al, John and Jack go to the airport with the same car and Al selects the money saving option before they start moving. However they are late and Al does not connect the car to the power grid even though he has parked in the power grid station. At the end only a discount of 10\% will be applied, because there were two passengers other the driver.
\section{Scenario 5}
John and Jack reserve a car to go to the mall. There is not a safe area where to park near the mall so they park in the mall parking. The system will warn them that there it is not possible to end the rent. John and Jack can leave the car but the car is still reserved by them and they continue to pay the normal fee. Once they end shopping they return to the car and come back home, looking for a safe area where to end the rent.
\section{Scenario 6}
Carl decide to have an excursion and reserves a car to go to the lake. There is not a safe area near the lake so he parks near it without ending the rent. At the end of the day he decides to come back home with the train leaving the car there without ending the rent. 24 hours after the rent started, the system will end it and it will charge to Carl the full amount of rent fee with an additional fine.
\section{Scenario 7}
Carl, with his friend Joe and Debby, has an appointment through the city and they decide to rent a car. At some point he realizes the car has only 10\% power left and so he parks it in the nearest safe area and ends the rent. The system will charge Carl's account the final bill increased of 20\%. This because he gained a discount of 10\% taking two passengers on the car and a fine of 30\% because he did not connect the car to the power grid and left it with 10\% of battery.