\section{Product Functions}
%Summary of major functions. It's a sort of summary of the requirements. 
Product Functions.
\begin{description}
\item[Registration:] a non registered user registers to PowerEnJoy service providing the following data:
	\begin{itemize}
	\item name;
	\item surname;
	\item username;
	\item e-mail address;
	\item date of birth;
	\item sex;
	\item country of birth;
	\item phone number;
	\item province of birth;
	\item tax id code; % English for Italian "codice fiscale"
	\item document information, that has to be validated;
	\item residential address;
	\item living address;
	\item payment information.
	\end{itemize}
	The user will receive back a password that can be used to access the system.
\item[Login:] a user accesses the system using the e-mail address they provided in the registration and the password they received.
\item[Edit profile data:] a user deletes their data, to keep them updated for example.
\item[Delete account:] a user deletes his account.
\item[Look for a car with user position:] a user look for a car basing the research on their devices position.
\item[Look for a car with a specified address:] a user look for a car basing the research on a specific address.
\item[Reserve a car:] a user book a car that he/she found in a previous research. He/she has up to one hour of time to reach the car and unlock it, otherwise the reservation expires and he/she has to pay a fee of 1 EUR.
%I am not sure if to include "unlock a car" and "start the car" in this section
\item[Unlock a car:] a user unlocks a car that he previously reserved at maximum one hour before. This option will be available to the user only if the GPS of his/her device is recognized at maximum at 6 meters from the car.
\item[Start the car:] a user that has unlocked the car starts the engine of the car by inserting his password in the tablet of the car
\item[Know the current fee:] a user looks at the tablet of the car and reads the current fee. He/she can do this in every moment when he/she is in the vehicle, because the current fee is always displayed.
\item[Recharge the car:] a user connects the car to a plug of a power grid station.
\item[Enable saving money option:] a user enables the money saving option by clicking on the corresponding button in the tablet interface. At this point, he/she can input his/her final destination and the system provides information about the station where to leave the car to get a discount.
This station is determined to ensure a uniform distribution of cars in the city and depends both on the destination of the user and on the availability of power plugs at the selected station. 
\item[End the ride:] the system stops charging the user as soon as the car is parked in a safe area and the user exits the car.
\end{description}
