\section{Elements to be Integrated}
In the following paragraph we are going to provide a list of all the components that need to be integrated together.

The integration process of our software is performed on two levels.
\begin{enumerate}
\item \textbf{Low Level:} Integration of the different subcomponents (classes, Java Beans) inside the
same subsystem;
\item \textbf{High Level:} Integration of different subsystems.
\end{enumerate}

The first step needs to be performed only for the components which contains
the pieces of software that we are going to develop, namely the business
tier, the mobile application in the client tier.

In particular the main subcomponents that we will integrate are:
\begin{itemize}
\item \textbf{User Manager:} This subcomponent includes Registration, Login, Edit Profile and User Banning;
\item \textbf{Email Sender};
\item \textbf{Operator Safe Area Manager:} This subcomponent includes Add Safe Area, Delete Safe are, Add Power Grid Station and Delete Power Grid Station;
\item \textbf{User Safe Area Manager}
\item \textbf{Ride Manager:} This subcomponent includes Update Ride Status and End Ride;
\item \textbf{Car Manager:} This subcomponent includes Reserve Car, Update Position and Unlock Car;
\item \textbf{Fee Manager:} This subcomponent include Enable Saving Money Option and Disable Saving Money Option;
\item \textbf{Payment Manager:} This subcomponent include Pay Ride and Check Payment Info;
\end{itemize}


The second step needs to be performed on the three major high-level components that we outlined in the Design Document, that correspond to the tiers of the system, which – from now on – will
be referred to as subsystems:
\begin{itemize}
\item \textbf{Client tier:} The client tier consists of our mobile application, the operator terminal and the on-board tablet.
\item\textbf{Business tier:} This subsystem implements all the application logic, communicates with the front-ends and the external systems.
\item \textbf{Database tier:} This is the DBMS, it is not part of the software to be developed,
but has to be integrated.
\end{itemize}
It is important to underline that the business tier needs to be integrated with some external systems that we will consider as black box, because we are not going to develop them but just to integrate them.

These external systems are the following:
\begin{itemize}
\item \textbf{Handy Car Board};
\item \textbf{External System For Driving License Validation};
\item \textbf{External System For Payments}.
\end{itemize}


