\section{Actors}
The actors of our system are the visitors, the users and the maintainers of the company.
%TODO finish this session
\subsection{Non Registered User}
A Non Registered User is a person who is not logged in to the system. The functionality that he/she is able to do is the registration.

In order to register to PowerEnJoy service, the Non Registered User must provide the following data:
\begin{itemize}
	\item name
	\item surname
	\item username
	\item password
	\item e-mail address
	\item date of birth
	\item sex
	\item country of birth
	\item phone number
	\item province of birth
	\item tax id code % English for Italian "codice fiscale"
	\item driving license
	\item document information
	\item residential address
	\item living address
	\item payment information;
\end{itemize}

The phone number is accepted as it is, the e-mail address must be validated with a token and all
the other data must be validated by the proper authorities.

\subsection{User}
A user is a person who logged in to the system. He can access to the following functionalities:
\begin{itemize}
	\item book a car
	\item ...
\end{itemize}

\subsection{Driver}
A driver is a special case user that opened the car and inserted his password on the screen. He has access to the following functionalities:
\begin{itemize}
	\item money saving option (insert destination and receive nearest power grid station);
	\item park the car in a safe area.
\end{itemize}

\subsection{Maintainer}
A maintainer is an employee that has to charge the cars with a battery level under 25\% and to repair the broken components (electronic or mechanical) of the cars. He has also to return all the cars left outside a safe area in a safe one.