\section{Scope}
%Identifies the product and application domain. analysis of the world and of the shared phenomena.
The user can interact with the system with both a mobile app and a website.
Every car is equipped with a geo-localization system that allows to localize it through the GPS signal.
The system uses also the GPS of the mobile phone of the user, so when it is near to the car he can unlock it if he reserved it.

In order to become a user and to access the service, a person has to sign up to it, providing their credentials and payment information. If the registration is successful the user will receive back a password that can be used to access the system and to unlock the car.

The system knows the position and the battery level of all the available electric-cars, so the user can choose what car to reserve based on these two factors. If a user book a car, the system reserve that car to that user therefore, for a certain period of time, that car will not be available to other users.

On board of the vehicle the user will find a tablet that can be used as a navigator, to see the amount of the current fee and in general to interact with the service. In particular, in the navigator and in the map of the mobile application, some zone of interests are highlighted: the safe areas. These special places are the the only areas in which the users can leave the car in order to end their reservation. In fact, the system stops charging the user as soon as the car is parked in a safe area and the user exits the car.

Inside some safe areas there are the power grid stations, where the user can recharge their car. If the user takes care of plugging the car into the power grid when he end his reservation, the system applies a discount of 30\% on the last ride.
