\section{Definitions, acronyms, abbreviations}
\begin{description}
    \item[JPA:] The Java Persistence API (JPA) is a Java application programming interface specification that describes the management of relational data.
    \item[MySQL:]It is an open-source relational database management system,the term SQL is the abbreviation for Structured Query Language.
    \item[InnoDB:]It is a storage engine for MySQL. MySQL 5.5 and later use it by default
    \item[ACID:]It is a set of properties of database transactions: Atomicity,Consistency,Isolation,Durability.
    \item[ER:]The entity–relationship(ER) model,it describes inter-related things of interest in a specific domain of knowledge
    \item[EJB:]Enterprise JavaBeans (EJB) is a managed, server software for modular construction of enterprise software, and one of several Java APIs.
    \item[JPQL:]The Java Persistence Query Language (JPQL) is a platform-independent object-oriented query language defined as part of the Java Persistence API (JPA) specification.
    \item[JAX-RS:]Java API for RESTful Web Services (JAX-RS) is a Java programming language API spec that provides support in creating web services according to the Representational State Transfer (REST) architectural pattern.
    \item[RESTful:]Representational state transfer (REST) or RESTful web services are one way of providing interoperability between computer systems on the Internet.
    \item[JSON:]JSON (JavaScript Object Notation) is a lightweight data-interchange format.
    \item[RASD:] Requirements Analysis and Specification Document.
\end{description}
